---
title: "2016-0509 MSDS 6304 Week 4 Homework"
author: "Bill Kerneckel"
date: "May 27, 2016"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
<br>
<br>
<strong><u>Assignment:</u></strong><br>

Write bootstrap code to illustrate the central limit theorem in R markdown and push the result to GitHub. Use a <strong>normal distribution</strong> with two different sample sizes and an <strong>exponential distribution</strong> with two different sample sizes. Please also comment on the code and explain the results. 

------------
<br>
<strong>Step 1:</strong> Generate normal distribution with two different sample sizes
<br>
```{r}
x <- rnorm(50, 22, 5)
y <- rnorm(50,25,5)
x1 <- c(x)
y2 <- c(y)
z <- c(x1,y2)
```
<br>
<strong>Step 2:</strong> Now lets output the combined 'z' sample size to see if our above statements worked.
<br>
```{r}
z
```
<br>
<strong>Step 3:</strong> Lets take the mean of the 'z' sample size.
<br>
```{r}
zbar <- mean(z)
zbar
```
<br>
<strong>Step 4:</strong> Lets apply the bootstrap principal to illustrate the centeral limit theorem. First we need to set the repetitions to 1000.
<br>
```{r}
nsims <- 1000
```
<br>
<strong>Step 5:</strong> Now we need to loop 1000 repetitions through the combined 'z' sample size of 100. In the loop the following occurs:
  
1. Pulls one value from the 'z' sample size
2. Puts the one value back into the orginal 'z' sample population
3. Calculates 1000 means
<br>
<br>
```{r}
bootnorm <- numeric(nsims)
 	for (i in 1:nsims) {
	temp <- sample (z, 100, replace=TRUE)
	bootnorm[i] <- mean(temp)
 	}
```
<br>
<strong>Step 6:</strong> Lets see the summary of the bootstrap simulation.
<br>
```{r}
summary(bootnorm)
```
<br>
<strong>Step 7:</strong> Now we can compare the bootstrap mean to the orginal mean of the 'z' sample size. You notice how close they are of being equal to each other. Lets compare the standard deviations of the orginal 'z' sample and of the bootstrap data.
<br>
<br>
'z' Sample Standard Deviation<br>
```{r}
sd(z)
```
<br>
Bootnorm Sample Standard Deviation<br>
<br>
```{r}
sd(bootnorm)
```
<br>
<strong>Step 8:</strong> If we take the standard deviation of the orginal 'z' samples size and divide it by the square root of the 'z' sample size off 100 the results should be the same as the orginal standard deviation of the 'z' sample. By comparing the two demostrates the central limit theorem.
<br>
```{r}
sd(z)/sqrt(100)
```
<br>
<hr>
<p>The next part of the home work assignment was to demostrate using a exponential distribution with two different sample sizes.</p>
<br>
<br>
<strong>Step 1:</strong> Generate normal distribution with two different sample sizes
<br>
```{r}
d <- rnorm(50, 22, 5)
e <- rnorm(50,25,5)
d1 <- c(d)
e2 <- c(e)
f <- c(d1,e2)
```
<br>
<strong>Step 2:</strong> Now lets output the combined 'f' sample size to see if our above statements worked:
<br>
```{r}
z
```
<br>
<strong>Step 3:</strong> Lets take the mean of the 'f' sample size.
<br>
```{r}
fbar <- mean(f)
fbar
```
<br>
<strong>Step 4:</strong> Lets apply the bootstrap principal to illustrate the centeral limit theorem. First we need to set the repetitions to 1000.
<br>
```{r}
nsims <- 1000
```
<br>
<strong>Step 5:</strong> Now we need to loop 1000 repetitions through the combined 'f' sample size of 100. In the loop the following occurs:
  
1. Pulls one value from the 'f' sample size
2. Puts the one value back into the orginal 'f' sample population
3. Calculates 1000 means
<br>
<br>
```{r}
bootnorm <- numeric(nsims)
 	for (i in 1:nsims) {
	temp <- sample(f, 100, replace=TRUE)
	bootnorm[i] <- mean(temp)
 	}
```
<br>
<strong>Step 6:</strong> Lets see the summary of the bootstrap simulation.
<br>
```{r}
summary(bootnorm)
```
<br>
<strong>Step 7:</strong> Now we can compare the bootstrap mean to the orginal mean of the 'f' sample size. You notice how close they are of being equal to each other. Lets compare the standard deviations of the orginal 'f' sample and of the bootstrap data.
<br>
<br>
'f' Sample Standard Deviation<br>
```{r}
sd(f)
```
<br>
Bootnorm Sample Standard Deviation<br>
<br>
```{r}
sd(bootnorm)
```
<br>
<strong>Step 8:</strong> If we take the standard deviation of the orginal 'f' samples size and divide it by the square root of the 'f' sample size off 100 the results should be the same as the orginal standard deviation of the 'f' sample. By comparing the two demostrates the central limit theorem.
<br>
```{r}
sd(f)/sqrt(100)
```

  
